IML Term project

### 2022-12-03 main_markdown.rmd
git correlation update

# First level title
## Second level title
### etc.

>>>>

## Correlations

```{r correlations}
library(corrplot)

npfOrig <- read.csv("npf_train.csv")
npfOrig$class2[npfOrig$class4 == "nonevent"] <- 0
npfOrig$class2[npfOrig$class4 != "nonevent"] <- 1

# Select global and 16.8 m high values
npf <- data.frame(npfOrig[, (5:6)], npfOrig[, (13:16)], npfOrig[, (27:30)], 
                  npfOrig[, (41:42)], npfOrig[, (53:54)], npfOrig[, (63:72)],
                  npfOrig[, (83:88)], npfOrig[, (99:104)])

# Calculate the correlation matrix
cm <- cor(npf)

# Order variables by 1st principal component
corrplot(cm, order = "FPC", tl.cex = 0.5, tl.col = "black")
```
